\stktokens{}: Enforcing Well-Bracketed Control Flow and Stack Encapsulation Using Linear Capabilities

### 2019-07-29 popl-2019-journal-v/discussion.tex
Rewrite discussion about reasonable/well-formed
Split the discussion in two, so they are not lumped together.

  % Say something about horizontal vs vertical composition.
  Fully-abstract compilers compose vertically which means that if we defined a compiler phase that targets \srccm{}, then we could use the full-abstraction theorem immediately.
  However, fully-abstract compilers do not extend horizontally in the sense that if we add a new feature in the target and source language, then the full-abstraction theorem does not follow immediately.
  \dominique{I find this ``vertical extensionality'' both vague and unrealistic. Should we really discuss this?}
  Intuitively, this is the case because the new feature may have an unforeseen interaction with existing features that breaks a desired property.
  In order to enforce more language properties on capability machines, it is reasonable to assume that new capability primitives may be necessary.
  \stktokens{}, for instance, requires linear capabilities, and \citet{skorstengaard_reasoning_2017} uses local capabilities to enforce WBCF and LSE.
  In order to implement address-hiding (i.e.\ have references that do not expose the address they actually point to), it is reasonable to believe that one would need a new capability primitive.
  After all, the capabilities we use here do not hide the addresses in any meaningful way, so a new ``address hiding'' capability would be necessary to enforce this property.
  If we extended \trgcm{} and \srccm{} with new such capabilities, then we would have to redo the entire full-abstraction proof.

  % new paragraph: conditional full-abstraction
  \dominique{This paragraph should perhaps also point out the link to the dynamic compromise paper?}
  Our full-abstraction theorem, Theorem~\ref{thm:full-abstraction}, is not pure full-abstraction as it requires the components to be reasonable and well-formed.
  In other words, if we were to define a compiler phase that targets \srccm{}, then we would also have to show that every program it generates is well-formed and reasonable in order to use the full-abstraction result.
  \dominique{The word ``however'' is wrong in the next sentence.  IIUC, you're explaining *why* we require the previous compiler phase to have ensured reasonability instead of enforcing reasonability in StkTokens.
  This is very confusing.}
  \dominique{Also: I'm not sure it's a good idea to lump together reasonability and well-formedness.
    In my understanding, well-formedness is a set of *syntactic* constraints and the requirement that the linker has distributed seals properly.
    As such, the discussion below seems to be only about reasonability, not well-formedness.
  }
  However, even though the well-formed and reasonable conditions are fairly simple, it is too late to ensure them at this point of the compilation.
  For instance, reasonability require that return seals are not passed to the adversary in calls.
  In order to ensure this with \stktokens{}, we would have to add checks to the calling convention that ensures that seals are not passed as arguments in calls.
  In other words, we would need to add protection to the trusted program against itself which of course shouldn't be necessary.
  The calling convention should only include protection schemes that protects against untrusted programs.
  The compiler should generate programs that are actually trustworthy, so we do not have to add protection against the generated programs.
  However, when we consider \srccm{} components, we have already committed to a program consisting of low-level instructions.
  The correct place to ensure that our programs are well-formed and reasonable is when we actually generate the instructions and commit to the low-level code which is the phase that goes from the high-level language (or some intermediate representation) to a low-level machine like \srccm{}.

>>>>

\begin{thesisonly}
  % Say something about horizontal vs vertical composition.
  Fully-abstract compilers compose vertically which means that if we defined a compiler phase that targets \srccm{}, then we could use the full-abstraction theorem immediately.
  However, fully-abstract compilers do not extend horizontally in the sense that if we add a new feature in the target and source language, then the full-abstraction theorem does not follow immediately.
  Intuitively, this is the case because the new feature may have an unforeseen interaction with existing features that breaks a desired property.
  In order to enforce more language properties on capability machines, it is reasonable to assume that new capability primitives may be necessary.
  \stktokens{}, for instance, requires linear capabilities, and \citet{skorstengaard_reasoning_2017} uses local capabilities to enforce WBCF and LSE.
  In order to implement address-hiding (i.e.\ have references that do not expose the address they actually point to), it is reasonable to believe that one would need a new capability primitive.
  After all, the capabilities we use here do not hide the addresses in any meaningful way, so a new ``address hiding'' capability would be necessary to enforce this property.
  If we extended \trgcm{} and \srccm{} with such new capabilities, then we would have to redo the entire full-abstraction proof.
\end{thesisonly}

  % new paragraph: conditional full-abstraction
  \dominique{This paragraph should perhaps also point out the link to the dynamic compromise paper?}
  Our full-abstraction theorem, Theorem~\ref{thm:full-abstraction}, is not pure full-abstraction as it requires the components to be reasonable and well-formed.
  In other words, if we were to define a compiler phase that targets \srccm{}, then we would also have to show that every program it generates is well-formed and reasonable in order to use the full-abstraction result.
  Without the reasonability constraint, \stktokens{} would have to enforce reasonability instead.
  That is, \stktokens{} would have to dynamically ensure that no return seals or means to get return seals are passed in calls.
  Essentially, such checks would protect the trusted code against itself which shouldn't be necessary in the first place.
  Instead, the compiler should generate reasonable code that never exhibits the unreasonable behaviour.
  This should be done in a compiler phase where more information about the original program is available, e.g.\ the compilation phase that commits to the low-level translation.
  Similarly for the syntactic constraints given by well-formedness.
  The compiler should make sure to generate code that satisfies the well-formedness judgement, so it can be executed by the machine.
